DisCon Kids Pilot

### 2019-02-23 analysis/01_adult_speakerchange_preference.Rmd
update kids 600 analysis

child_waic <- brms::WAIC(bm1, bm2, compare = F)

child_weights <- model_weights(bm1, bm2)

@@

```
## Model comparison using WAIC and Bayes Factor
```{r}
data_frame(
  model = c("bm1_w_condition","bm2"),
  WAIC = c(child_waic$bm1$estimates[3,1],child_waic$bm2$estimates[3,1]),
  SE = c(child_waic$bm1$estimates[3,2],child_waic$bm2$estimates[3,2]),
  weight = c(child_weights[1],child_weights[2]),
  BF_bm1_bm2 = c(round(bf_full_null$bf,2),"-"))%>%
  kable(digits = 2)
```

>>>>

waic <- brms::WAIC(bm1, bm2, compare = F)

weights <- model_weights(bm1, bm2)

@@

```
## Model comparison using WAIC and Bayes Factor
```{r}
data_frame(
  model = c("bm1_w_condition","bm2"),
  WAIC = c(waic$bm1$estimates[3,1],waic$bm2$estimates[3,1]),
  SE = c(waic$bm1$estimates[3,2],waic$bm2$estimates[3,2]),
  weight = c(weights[1],weights[2]),
  BF_bm1_bm2 = c(round(bf_full_null$bf,2),"-"))%>%
  kable(digits = 2)
```

### 2019-02-23 analysis/02_kids_600.Rmd
update kids analysis file
update kids 600 analysis

library(tidyverse)
library(ggplot2)
library(jsonlite)
library(tidyr)
library(stringr)
library(dplyr)
library(ggthemes)
library(langcog)
library(readxl)

@@

p4 <- p1 %>%
  multi_boot_standard(col = "correct")

@@

ggplot(data = p5, aes(x = age_num, y = correct)) +
  geom_jitter(width = .0,height = .0, alpha = .5)+
  geom_smooth(method = "lm",  se = T,  alpha = .5, size = .6, span = 2)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="Age",y="Proportion correct choice")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(3,5)+
  guides(alpha = F)
```

>>>>

library(tidyverse)
library(ggplot2)
library(jsonlite)
library(tidyr)
library(stringr)
library(dplyr)
library(ggthemes)
library(langcog)
library(readxl)
library(knitr)

@@

p4 <- p3 %>%
  group_by(subage) %>%
  multi_boot_standard(col = "correct")

@@

ggplot(data = p5, aes(x = age_num, y = correct)) +
  geom_jitter(width = .01,height = .01, alpha = .5)+
  geom_smooth(method = "lm",  se = T,  alpha = .5, size = .6, span = 2)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="Age",y="Proportion correct choice")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(3,5)+
  guides(alpha = F)
```

# Bayesian t-test against chance across age groups

```{r}
## one sample bayesian t-tests
library(BayesFactor)

data %>%
  filter(phase != "training") %>%
  group_by(subage, subid) %>%
  summarise(correct = mean(correct_target1)) %>%
  summarise(correct = list(correct)) %>%
  group_by(subage) %>%
  mutate(mean= mean(unlist(correct)),
         bf = extractBF(ttestBF(unlist(correct), mu = 1/3))$bf) %>%
  select(subage,mean,bf) %>%
  knitr::kable(digits = 3)

samples = ttestBF(x$correct, mu = 1/3, posterior = T, iterations = 1000)

# Model 
```{r}
library(brms)

model_data <- data%>%
  filter(phase == "test")%>%
  mutate(age_num = scale(age_num))

mean(model_data$age_num)

#   model

kbm1 <- brm(correct_target1 ~ age_num +
                      (1| subid) + (1 | target1),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.95),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 2000)

summary(kbm1)
```

```{r}
bayesplot::mcmc_areas(as.array(kbm1), pars = c("b_Intercept", "b_age_num"), prob = 0.95)+
  geom_vline(xintercept = 0, lty = 2, col = "black")+
  theme_few()
```

```{r}
kbm2 <- brm(correct_target1 ~ 1 +
                      (1| subid) + (1 | target1),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.95),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 2000)

summary(kbm2)
```

## Model comparison

```{r}
child_waic <- brms::WAIC(kbm1, kbm2, compare = F)

child_weights <- model_weights(kbm1, kbm2)

# Bayes Factors (slightly variable)
bf_full_null <- bayes_factor(kbm1, kbm2, log = FALSE, maxiter = 5000)
```

```{r}
data_frame(
  model = c("kbm1_w_age","kbm2"),
  WAIC = c(child_waic$kbm1$estimates[3,1],child_waic$kbm2$estimates[3,1]),
  SE = c(child_waic$kbm1$estimates[3,2],child_waic$kbm2$estimates[3,2]),
  weight = c(child_weights[1],child_weights[2]),
  BF_bm1_bm2 = c(round(bf_full_null$bf,2),"-"))%>%
  kable(digits = 2)
```
